---
title: "In-class_Ex01"
author: "Lin Lin"
---

```{r}
pacman::p_load(tidyverse)
```

## Importing the data

(data will load in environment)

```{r}
exam_data <- read_csv("data/Exam_data.csv")


```

### Plot the diagram with filliped diagram coordinate and background

```{r}
ggplot(data = exam_data,
       aes(x = RACE)) +
         geom_bar() + 
        coord_flip() +
        theme_minimal()+
        theme(panel.background = element_rect(fill = "lightblue", colour = "lightblue", linetype = "solid"))
```
### Make the visualization better by y axis
- y-aixs label is not clear (i.e. count)
- To support effective comparison, the bars should be sorted by their resepctive frequencies.
- For static graph, frequency values should be added to provide addition information.

```{r}

ggplot(data = exam_data,
       aes(x=reorder(RACE,RACE,
                     function(x) -length(x)))) +
         geom_bar() + 
        ylim(0,220) +
        theme_minimal()+
        theme(panel.background = element_rect(fill = "lightblue", colour = "lightblue", linetype = "solid")) + 
 geom_text(stat="count", 
      aes(label=paste0(..count.., ", ", 
      round(..count../sum(..count..)*100, 1), "%")),
      vjust=-1) +
  xlab("Race") +
  ylab("No. of\nPupils")


```

### Use fct_infreq() to to sort
 mutate(RACE = fct_infreq(RACE)) %>%


```{r}
exam_data %>%
  mutate(RACE = fct_infreq(RACE)) %>%
  ggplot(aes(x = RACE)) + 
  geom_bar()+
  ylim(0,220) +
  geom_text(stat="count", 
      aes(label=paste0(..count.., ", ", 
      round(..count../sum(..count..)*100,
            1), "%")),
      vjust=-1) +
  xlab("Race") +
  ylab("No. of\nPupils") +
  theme(axis.title.y=element_text(angle = 0))


```

### Plot math with histogram diagram

Add in dashed line for mean and median value
and fill color use light blue, change border color black


```{r}
ggplot(data=exam_data, 
       aes(x= MATHS)) +
  geom_histogram(bins=20, 
                 color="black", 
                 fill="light blue") +
  geom_vline(aes(xintercept=mean(MATHS, na.rm=T)),
             color="red", 
             linetype="dashed", 
             size=1) +
  geom_vline(aes(xintercept=median(MATHS, na.rm=T)),
             color="grey30",
             linetype="dashed", 
             size=1)
```

### Overlay histograms 
- The background histograms show the distribution of English scores for all pupils.

- facet_wrap according to gender

```{r}
d <- exam_data   
d_bg <- d[, -3]  

ggplot(d, aes(x = ENGLISH, fill = GENDER)) +
  geom_histogram(data = d_bg, fill = "grey", alpha = .5) +
  geom_histogram(colour = "black") +
  facet_wrap(~ GENDER) +
  guides(fill = FALSE) +  
  theme_bw()
```


### Overlay the scatter diagram with axis

- 
```{r}
ggplot(data=exam_data, 
       aes(x=MATHS, y=ENGLISH)) +
  geom_point() +
  coord_cartesian(xlim=c(0,100),
                  ylim=c(0,100)) +
  geom_hline(yintercept=50,
             linetype="dashed",
             color="grey60",
             size=1) + 
  geom_vline(xintercept=50, 
             linetype="dashed",
             color="grey60",
             size=1)

```
