---
title: "Hands-on_Ex04Chpt10"
author: "Lin Lin"
---

## Visualizing the uncertainty of point estimates

-   A point estimate is a single number, such as a mean.

-   Uncertainty is expressed as standard error, confidence interval, or credible interval

-   Important:

-   Don't confuse the uncertainty of a point estimate with the variation in the sample

```{r}
    #| warning: false
pacman::p_load(tidyverse, plotly, crosstalk, DT, ggdist, gganimate)
exam <- read_csv("data/Exam_data.csv")

```

### Visualizing the uncertainty of point estimates: ggplot2 methods

-   group the observation by RACE,

-   computes the count of observations, mean, standard deviation and standard error of Maths by RACE, and

-   save the output as a tibble data table called `my_sum`.

```{r}
    #| warning: false
  my_sum <- exam %>%
    group_by(RACE) %>%
    summarise(
      n=n(),
      mean=mean(MATHS),
      sd=sd(MATHS)
      ) %>%
    mutate(se=sd/sqrt(n-1))

  knitr::kable(head(my_sum), format = 'html')
```


### Visualizing the uncertainty of point estimates: ggplot2 methods
below is how reveal the standard error of mean maths score by race.
```{r}
  ggplot(my_sum) +
  geom_errorbar(
    aes(x=RACE, 
        ymin=mean-se, 
        ymax=mean+se), 
    width=0.2, 
    colour="black", 
    alpha=0.9, 
    size=0.5) +
  geom_point(aes
           (x=RACE, 
            y=mean), 
           stat="identity", 
           color="red",
           size = 1.5,
           alpha=1) +
  ggtitle("Standard error of mean 
          maths score by rac")

```
