---
title: "Hands-on_Ex08B"
author: "LIN LIN"
---

# **Analytical Mapping**

This document is about ploting analytical maps with the following steps:

-   Importing geospatial data in rds format into R environment.

-   Creating cartographic quality choropleth maps by using appropriate tmap functions.

-   Creating rate map

-   Creating percentile map

-   Creating boxmap

## Load Library and Data

```{r load library}
  pacman::p_load(tmap, tidyverse, sf)
```

```{r loadData}
  NGA_wp <- read_rds("data/rds/NGA_wp.rds")
```

## **Basic Choropleth Mapping**

```{r}
  p1 <- tm_shape(NGA_wp) +
  tm_fill("wp_functional",
          n = 10,
          style = "equal",
          palette = "Blues") +
  tm_borders(lwd = 0.1,
             alpha = 1) +
  tm_layout(main.title = "Distribution of functional water point by LGAs",
            legend.outside = FALSE)

  p2 <- tm_shape(NGA_wp) +
  tm_fill("total_wp",
          n = 10,
          style = "equal",
          palette = "Blues") +
  tm_borders(lwd = 0.1,
             alpha = 1) +
  tm_layout(main.title = "Distribution of total  water point by LGAs",
            legend.outside = FALSE)

  tmap_arrange(p2, p1, nrow = 1)
```

### Deriving Proportion of Functional Water Points and Non-Functional Water Points

We will tabulate the proportion of functional water points and the proportion of non-functional water points in each LGA. In the following code chunk, mutate() from dplyr package is used to derive two fields, namely pct_functional and pct_nonfunctional.

```{r }
  NGA_wp <- NGA_wp %>%
    mutate(pct_functional = wp_functional/total_wp) %>%
    mutate(pct_nonfunctional = wp_nonfunctional/total_wp)
```

#### map of rate

```{r }
tm_shape(NGA_wp) +
  tm_fill("pct_functional",
          n = 10,
          style = "equal",
          palette = "Blues",
          legend.hist = TRUE) +
  tm_borders(lwd = 0.1,
             alpha = 1) +
  tm_layout(main.title = "Rate map of functional water point by LGAs",
            legend.outside = TRUE)

```

### **Percentile Map**

The percentile map is a special type of quantile map with six specific categories: **0-1%,1-10%, 10-50%,50-90%,90-99%, and 99-100%.** The corresponding breakpoints can be derived by means of the base R quantile command, passing an explicit vector of cumulative probabilities as c(0,.01,.1,.5,.9,.99,1). Note that the begin and endpoint need to be included.

It's important to have 0 and 1 at the two ends.

We need to drop the drometry

#### Data Preparation

Step 1: Exclude records with NA by using the code chunk below.

```{r }
  NGA_wp <- NGA_wp %>%   drop_na()
```

Step 2: Creating customised classification and extracting values

```{r }
  percent <- c(0,.01,.1,.5,.9,.99,1) 
  var <- NGA_wp["pct_functional"] %>%   
  st_set_geometry(NULL) #this is to drop away the column geometry
quantile(var[,1], percent)
```

#### Creating the get.var function

Firstly, we will write an R function as shown below to extract a variable (i.e. *wp_nonfunctional*) as a vector out of an sf data.frame.

-   arguments:
    -   vname: variable name (as character, in quotes)
    -   df: name of sf data frame
-   returns:
    -   v: vector with values (without a column name)

```{r functionGetVariable}
  get.var <- function(vname,df) {   
    v <- df[vname] %>%     
    st_set_geometry(NULL)  #this is similar to drop the geometry column 
  v <- unname(v[,1])   
  return(v) 
  }
```

#### A percentile mapping function

Next, we will write a percentile mapping function by using the code chunk below.

```{r definePercentMapFunction}
  #here we write another funciton and later we will reuse it
  percentmap <- function(vnam, df, legtitle=NA, mtitle="Percentile Map"){
  percent <- c(0,.01,.1,.5,.9,.99,1) #define percent cutting
  var <- get.var(vnam, df) #run the funtion to create variable
  bperc <- quantile(var, percent) #this is the quantile created
  tm_shape(df) +
  tm_polygons() +
  tm_shape(df) +
     tm_fill(vnam, #input parameter
             title=legtitle,
             breaks=bperc, #the pair we created using function earlier
             palette="Blues",
          labels=c("< 1%", "1% - 10%", "10% - 50%", "50% - 90%", "90% - 99%", "> 99%"))  +
  tm_borders() +
  tm_layout(main.title = mtitle, 
            title.position = c("right","bottom"))
}
```

```{r testPercentileMap}
  percentmap("total_wp", NGA_wp)

```

### **Box map**

First, this is hoow it looks like when we plot normal boxplot:

```{r }
  ggplot(data = NGA_wp,
       aes(x = "",
           y = wp_nonfunctional)) +
  geom_boxplot()
```

#### Creating the boxbreaks function

The code chunk below is an R function that creating break points for a box map.

-   arguments:

    -   v: vector with observations

    -   mult: multiplier for IQR (default 1.5)

-   returns:

    -   bb: vector with 7 break points compute quartile and fences

```{r boxplotBreakPointFunction}
  boxbreaks <- function(v,mult=1.5) {
  qv <- unname(quantile(v)) #get the quatile value
  iqr <- qv[4] - qv[2] #calclating inter quantile range
  upfence <- qv[4] + mult * iqr
  lofence <- qv[2] - mult * iqr
  # initialize break points vector
  bb <- vector(mode="numeric",length=7)
  # logic for lower and upper fences
  if (lofence < qv[1]) {  # no lower outliers
    bb[1] <- lofence
    bb[2] <- floor(qv[1])
  } else {
    bb[2] <- lofence
    bb[1] <- qv[1]
  }
  if (upfence > qv[5]) { # no upper outliers
    bb[7] <- upfence
    bb[6] <- ceiling(qv[5])
  } else {
    bb[6] <- upfence
    bb[7] <- qv[5]
  }
  bb[3:5] <- qv[2:4]
  return(bb)
  }
```

#### Creating the get.var function

The code chunk below is an R function to extract a variable as a vector out of an sf data frame.

-   arguments:

    -   vname: variable name (as character, in quotes)

    -   df: name of sf data frame

-   returns:

    -   v: vector with values (without a column name)

```{r removeGeometryPrepareVariable}
  get.var <- function(vname,df) {
  v <- df[vname] %>% st_set_geometry(NULL)
  v <- unname(v[,1])
  return(v)
  }
```

Test and use the function

```{r usingFunction}
  var <- get.var("wp_nonfunctional", NGA_wp) 
  boxbreaks(var)
```

#### Boxmap function

The code chunk below is an R function to create a box map. - arguments: - vnam: variable name (as character, in quotes) - df: simple features polygon layer - legtitle: legend title - mtitle: map title - mult: multiplier for IQR - returns: - a tmap-element (plots a map)

```{r}
  boxmap <- function(vnam, df, 
                   legtitle=NA,
                   mtitle="Box Map",
                   mult=1.5){
  var <- get.var(vnam,df)
  bb <- boxbreaks(var)
  tm_shape(df) +
    tm_polygons() +
  tm_shape(df) +
     tm_fill(vnam,title=legtitle,
             breaks=bb,
             palette="Blues",
          labels = c("lower outlier", 
                     "< 25%", 
                     "25% - 50%", 
                     "50% - 75%",
                     "> 75%", 
                     "upper outlier"))  +
  tm_borders() +
  tm_layout(main.title = mtitle, 
            title.position = c("left",
                               "top"))
}
```

```{r staticmapWithBoxMap}
  tmap_mode("plot")
  boxmap("wp_nonfunctional", NGA_wp)
```
