---
title: "Hands-on_Ex08A"
author: "LIN LIN"
---

# **Visualising Geospatial Point Data**

Proportional symbol maps (also known as graduate symbol maps) are a class of maps that use the visual variable of size to represent differences in the magnitude of a discrete, abruptly changing phenomenon, e.g. counts of people. Like choropleth maps, you can create classed or unclassed versions of these maps. **The classed ones are known as range-graded or graduated symbols, and the unclassed are called proportional symbols, where the area of the symbols are proportional to the values of the attribute being mapped.** In this hands-on exercise, you will learn how to create a proportional symbol map showing the number of wins by Singapore Pools\' outlets using an R package called **tmap**.

# **Load Libraries and data**

```{r loadLibrary}
  pacman::p_load(sf, tmap, tidyverse)
```

```{r loadData}
  sgpools <- read_csv("data/aspatial/SGPools_svy21.csv")
  list(sgpools) 
```

## Creating a sf data frame from an aspatial data frame
The coords argument requires you to provide the column name of the x-coordinates first then followed by the column name of the y-coordinates.
The crs argument required you to provide the coordinates system in epsg format. EPSG: 3414 is Singapore SVY21 Projected Coordinate System. You can search for other country’s epsg code by refering to epsg.io.

```{r}
  sgpools_sf <- st_as_sf(sgpools, 
                       coords = c("XCOORD", "YCOORD"), #by right you should have x = xcoord, y = xxxx
                       crs= 3414)  #this is important to let the engine know about the crs - cordinate referencing system

  list(sgpools_sf)
  # from now there's a geometry collumn

```


#### Drawing Proportional Symbol Map

```{r interativemap}
  tmap_mode("view")
  tm_shape(sgpools_sf)+
  tm_bubbles(col = "red",
             size = 1,
             border.col = "black",
             border.lwd = 1)
```

To draw a proportional symbol map, we need to assign a numerical variable to the size visual attribute. The code chunks below show that the variable Gp1Gp2Winnings is assigned to size visual attribute.

```{r proportionalMap}
  tm_shape(sgpools_sf)+
  tm_bubbles(col = "red",
           size = "Gp1Gp2 Winnings",
           border.col = "black",
           border.lwd = 1)
```


#### give it a different colour
The proportional symbol map can be further improved by using the colour visual attribute. In the code chunks below, OUTLET_TYPE variable is used as the colour attribute variable.
```{r differentColor}
  tm_shape(sgpools_sf)+
tm_bubbles(col = "OUTLET TYPE",   #this is how we set it with different categorical data
          size = "Gp1Gp2 Winnings",
          border.col = "black",
          border.lwd = 1)
```


## Magic Map: Twin Brother - Synchronized map

An impressive and little-know feature of tmap’s view mode is that it also works with faceted plots. The argument sync in tm_facets() can be used in this case to produce multiple maps with synchronised zoom and pan settings.


```{r syncMap}
  tm_shape(sgpools_sf) +
  tm_bubbles(col = "OUTLET TYPE", 
          size = "Gp1Gp2 Winnings",
          border.col = "black",
          border.lwd = 1) +
  tm_facets(by= "OUTLET TYPE",
            nrow = 1,
            sync = TRUE)  #this is how you make the facets sync together

```


Important note: to work with shiny, use renderTmap() then you can enjoy it in the shiny app

